%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% HEADER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper, twocolumn, oneside, 11pt]{article}

\usepackage{fourier}
\usepackage[T1]{fontenc}

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{pdflscape} 
\usepackage{abstract}
\usepackage[ table ]{ xcolor }
\usepackage[square, comma, sort&compress, longnamesfirst]{natbib} %
\usepackage{subfigure}
\usepackage{setspace}
%\singlespacing %% 1-spacing (default)s
%\onehalfspacing
\newcommand{\degree}{$^{\circ}$\ }
%%% END Article customizations

%%% The "real" document content comes below...


\title{The saccadic flow baseline: Accounting for image-independent biases in fixation behaviour }

\author{Alasdair D. F. Clarke, Matthew J. Stainer, Ben Tatler \& Amelia R. Hunt}

\begin{document}

\twocolumn[
\maketitle
\begin{onecolabstract}
Much effort has been made to explain eye guidance during natural scene viewing. However, a substantial component of fixation placement appears to be a set of consistent biases in eye movement behaviour. We introduce the concept of \textit{saccadic flow}, a generalisation of the central bias that describes the image-independent conditional probability of making a saccade to $(x_{i+1},y_{i+1})$, given a fixation at $(x_i,y_i)$. We suggest that saccadic flow can be used as a useful prior when carrying out analysis of fixation locations, and can be used as a sub-module in models of eye movements during scene viewing. We demonstrate the utility of this idea by presenting bias-weighted gaze landscapes, and show that there is a link between the likelihood of a saccade under the flow model, and the salience of the following fixation. We also present a minor improvement to our central bias model (based on using a multivariate truncated Gaussian), and investigate the leftwards and coarse-to-fine biases in scene viewing. 
\end{onecolabstract}
]

\input{Introduction}
\input{ModellingFlow}
\input{UsingFlow}

\section{Discussion}
There has been much effort to generate a predictive model of human eye movements \citep{mit-saliency-benchmark,judd2009}. We propose the saccadic flow model as a robust prior for the image-content independent saccadic behaviour that is evident when people look at pictures \citep{tatler-vincent2009}. There are two ways in which models of eye movements may benfit from including such information. First, models may include saccadic flow in their calculation of spatial prediction. Understanding where someone is currently fixating in an image appears to dramatically influence where they will go next, meaning that as saccadic flow can be parametrically estimated from any point on an image, it may be that this can be used to weight models of low-level (i.e. visual conspicuity) and high-level (i.e. semantic interest) features. Thus, whether someone fixates one of two equally conspicuous, equally interesting objects may be simply determined by the way that the eyes \textit{tend} to move. 

The second potential utility of saccadic flow is to generate realistic control fixations with which to evaluate observed fixation data. In this way, saccadic flow can be thought of as a partner to the \cite{clarke-tatler2014} central bias, and we expect that in some cases, the simpler central bias will be sufficient (for example, when examining the overall distribution of fixations rather than the sequence of saccades). However we have demonstrated that while the flow model requires more parameters (we use 16 coefficients to track how each of the five truncated Gaussian parameters vary as as a function of $(x,y)$ - although many of them are $\approx 0$), it generalises well from one dataset to another and is a far better baseline for modelling a scan-path than the central bias.

There are two main limitations to our modelling work. Firstly, by using a truncated Gaussian we are unable to capture the skewed nature of the distribution of saccades originating from the corners (see Figure \ref{fig:empiricalSaccadicFlow}). We experimented with fitting a skew-normal distribution using the \texttt{sn} package for \texttt{R}, but met with limited success due to having to deal with the image boundaries. We expect this is one of the main reasons why our saccadic flow model generates saccades with on average greater amplitudes than those seen in empirical distributions. The second simplification is that by not taking the leftwards or coarse-to-fine biases into account, we are limiting the degree to which we can model the dynamics of human scan-paths.

The work presented here improves on recent models by \cite{clarke2016,leMeur-coutrot2016} by offering a parametric model that avoids coarsely partioning the data into large bins. We have demonstrated that the Saccadic Flow model generalises well to unseen test datasets, although this is only likely to hold for stimuli that are broadly similar to the images used to train the model (photohraphs of natural and manmade scenes). As we move away from photographic images to stimuli such as computer interfaces, we would expect the Flow model to offer a poor account of the data \citep{leMeur-coutrot2016}. While we have shown that the model performs well over a small range of tasks (freeviewing, scene description, object naming and visual search), we do observer differences in the log likelihood when different tasks are carried out while viewing the same images. 


\subsection{Conclusions}
Behavioural biases in eye movement are prevelant during scene viewing. Our saccadic flow model allows calculation of saccade likelihood across an image based on empirical data of how the eye tends to move in many different scene viewing conditions, with flow providing a strong fit to several datasets. There are a number of ways that flow can be developed, and we propose that gaining a better understanding of the saccadic biases underlying fixation behaviour can only be a positive for our search to understand why people look where they look.


\section*{Acknowledgements}

And mention grants. 

\section*{Author Contribution}

All authors co-wrote the paper. The saccadic flow model was developed by ADFC. The gaze landscapes and saliency analysis were done by MJS.

\appendix
\input{Dataset}

\bibliographystyle{plainnat}
\small
\bibliography{literature.bib}
\end{document}